Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2018-10-09 analysis/paper/paper.Rmd
Moved CSVs from derived_data to raw_data/CSVs

```{r DataInput, eval=TRUE, echo=FALSE, cache=TRUE}
if (system("git config user.email")=="mward2@swarthmore.edu") source("./scripts/data_retrievalSwarthmore.R")
else source("./scripts/data_retrievalNPS.R")

@@

Recommendations: work with GIS shop to clean up db, improve reporting & query support; shiny app; reproducible research scripts to generate automatic reports? Shiny app to interface?

>>>>

```{r DataInput, eval=TRUE, echo=FALSE, cache=TRUE}
# if (system("git config user.email")=="mward2@swarthmore.edu") source("./scripts/data_retrievalSwarthmore.R")
# else source("./scripts/data_retrievalNPS.R")

###########
# MADELEINE WILL REPLACE WITH CODE TO VARIOUS TABLES FROM CSV FILES
###########
```

@@

The current database is written in Microsoft Access version XX for 32-bit operating systems. Software and machine operating systems have advanced enough for this to cause unnecessary burdens for accessing and importing the data for analysis and reporting in common statistical analysis environments (e.g., R). Recommend the Park request the ARO GIS shop to convert the database to an uptodate software.

*JOEL: Talk to Angie about what this would entail.*

_Recommendations_ work with GIS shop to clean up db, improve reporting & query support; shiny app; reproducible research scripts to generate automatic reports? Shiny app to interface?
